Concurrent Programming in Harmony

### 2022-01-28 book/paper.tex
format
Updated book accordingly

Method <{wait}> adds the context of the thread to the bag.
This increments the number of threads in the bag with the same context.
<{wait}> then loops until that count is restored to the
value that it had upon entry to <{wait}>.
Method <{notify}> removes an arbitrary context from
the bag, allowing one of the threads with that context to
resume and re-acquire the lock associated with the monitor.
<{notifyAll}> empties out the entire bag, allowing all threads
in the bag to resume.

@@

\begin{figure}
\begin{code}
<{:inline:}>
def fork():
    atomically:
        let (r, ctx) = save True:
            result = r
            if r:
                go ctx (False, None)

>>>>

Method <{wait}> adds the context of the thread---used as a unique
identifier for the thread---to the bag,
incrementing the number of threads in the bag with the same context.
The Harmony <{save}> expression (\autoref{ap:context}) returns a tuple
containing a value (in this case `<{()}>' and the context of the thread.
<{wait}> then loops until that count is restored to the
value that it had upon entry to <{wait}>.
Method <{notify}> removes an arbitrary context from
the bag, allowing one of the threads with that context to
resume and re-acquire the lock associated with the monitor.
<{notifyAll}> empties out the entire bag, allowing all threads
in the bag to resume.

@@

\begin{figure}
\begin{code}
<{:const:fork}>
<{:inline:}>
def fork():
    atomically:
        let (r, ctx) = save True:
            result = r
            if r:
                go ctx (False, None)
